---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Roboto:ital,wght@0,100..900;1,100..900&display=swap');
body {
  font-family: 'Roboto';
  background: #ffe3fa;
  color: #1c1c1c
}

h {
  font-weight: bold;
}
```

## Insights from Morning and Afternoon Walks

```{r}
# Reading in data from Google sheet
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR5Uf3ELnGQUaZzKwXYqmsSmRhWxRNcUF-sCjbbtqIqpMMFmNzS5k4wD2w3N65SsQXM9Ykv9DRdccPm/pub?gid=1351670053&single=true&output=csv")

# Renaming data 
latest_data <- logged_data %>%
                  rename(people_passed = 2,
                         weather = 3,
                         mood_after = 4,
                         main_activity = 5) 

# Minimum number of people passed 
min_peoplePassed <- min(latest_data$people_passed, na.rm = TRUE)
  
# Maximum number of people passed 
max_peoplePassed <- max(latest_data$people_passed, na.rm = TRUE)
  
# Average mood after walking
av_mood <- mean(latest_data$mood_after, na.rm = TRUE) %>%
                  round()

# Most frequent weather while walking
most_frequentWeather <- latest_data %>%
                          count(weather) %>%
                          arrange(desc(n)) %>%
                          slice(1)
# Most frequent activity 
most_frequentActivity<- latest_data %>%
                          count(main_activity) %>%
                          arrange(desc(n)) %>%
                          slice(1)
  
# Grouping number of people passed by weather
weather_people_summary <- latest_data %>%
                          group_by(weather) %>%
                          summarise(total_people = sum(people_passed, na.rm = TRUE))
 
# Bar chart of Weather vs. Number of people passed       
weather_people_chart <- ggplot(weather_people_summary, aes(x = reorder(weather, -total_people), y = total_people, fill = weather)) +
  geom_bar(stat = "identity") +
  labs(title = "Weather vs Total Number of People Passed",
       x = "Weather",
       y = "Total Number of People") +
  theme(legend.position = "none")

# Grouping number of people passed by main activity
activity_people_summary <- latest_data %>%
    group_by(main_activity) %>%
    summarise(total_people = sum(people_passed, na.rm = TRUE))
                            
# Bar chart of Main activity vs. Number of people passed
activity_people_chart <- ggplot(activity_people_summary, aes(x = reorder(main_activity, -total_people), y = total_people, fill = main_activity)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of People vs Main Activity",
       x = "Main Activity",
       y = "Total Number of People") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "none")
  
```

### Nature of my data
The nature of my data revolves around observations from morning and afternoon walks. Including:

-   Mood after walking

-   Main activity people were doing

-   What the weather was like

-   How many people were passed during the walk

### Analysis from my data
The following analysis was made:

-   The maximum number of people passed on a walk was `r max_peoplePassed`

-   The minimum number of people passed on a walk was `r min_peoplePassed`

-   The average mood felt after walking was a `r av_mood` out of 5.

-   The most frequent weather condition was `r most_frequentWeather$weather`.

-   The most frequent activity of people walking by was `r most_frequentActivity$main_activity`.

### Bar charts created from my data
```{r}
activity_people_chart
```

```{r}
weather_people_chart
```

