---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

## Insights from Morning and Afternoon Walks

```{r}
# Reading in data from Google sheet
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR5Uf3ELnGQUaZzKwXYqmsSmRhWxRNcUF-sCjbbtqIqpMMFmNzS5k4wD2w3N65SsQXM9Ykv9DRdccPm/pub?gid=1351670053&single=true&output=csv")

# Renaming data 
latest_data <- logged_data %>%
                  rename(people_passed = 2,
                         weather = 3,
                         mood_after = 4,
                         main_activity = 5) 

# Minimum number of people passed 
min_peoplePassed <- min(latest_data$people_passed, na.rm = TRUE)
  
# Maximum number of people passed 
max_peoplePassed <- max(latest_data$people_passed, na.rm = TRUE)
  
# Average mood after walking
av_mood <- mean(latest_data$mood_after, na.rm = TRUE) %>%
                  round()
```

### Nature of my data
The nature of my data revolves around observations from morning and afternoon walks. Including:

-   Mood after walking

-   Main activity people were doing

-   What the weather was like

-   How many people were passed during the walk

### Analysis from my data
The following analysis was made:

-   The maximum number of people passed on a walk was `r max_peoplePassed`

-   The minimum number of people passed on a walk was `r min_peoplePassed`

-   The average mood felt after walking was a `r av_mood` out of 5.


